% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage[document]{ragged2e}
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 
\begin{document} 
\name{
	\hspace{3 mm}ARTHUR NORMAND \\
	\hspace{17 mm}(908) 902-2202 \\
	\hspace{11 mm}Arthur@normand.space \\
	\hspace{0 mm}117 Agress Road, Millstone, NJ 08510
}
\begin{resume}
%\section{JOB OBJECTIVE}          
%    A summer position that will allow me to use and develop my programming and analytical skills       
%    \vspace{-0.2in}   
\section{EDUCATION}
	\vspace{-0.1in}
	\begin{tabbing}
		\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions  
		{\bf University of Massachusetts Amherst} \>\> Fall 2017\\
%		{\bf University of Massachusetts Amherst} Fall 2017\\
		Dean's List of Distinguished Students
		Bachelor of Science in Computer Science \\
		Concentration in Systems and Networks \\
		{\bf GPA 3.81/4.0}    
	\end{tabbing}
\vspace{-0.3in}
\section{WORK EXPERIENCE}
	% SMALL BUSINESS CONSULTANT
	\vspace{-0.1in}
	\begin{tabbing}
		\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
		{\bf Small Business Consultant}  \>Normand Consulting L.L.C. \> Summer 2009 - Present \\
			\>Clarksburg, NJ
	\end{tabbing}\vspace{-20pt}            % suppress blank line after tabbing
	Assist start-ups in making their business more efficient through the use of technology. Typically optimizing workflows, automating tasks and designing new systems.
	% ASSISTANT DIRECTOR OF IT
	\vspace{-0.2in}
	\begin{tabbing}
		\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
		{\bf Assistant Director of IT - NJ}  \>Beasly Media Group Inc.\> June 2017 - August 2017\\
			\>Clarksburg, NJ
	\end{tabbing}\vspace{-20pt}            % suppress blank line after tabbing
	Responsible for day to day business operations of an enterprise network with approximately 500 devices connected. Tasked with inventorying entire state's technology assets, installing distributed anti-virus software, deploying 		new endpoints to employees and building new systems for custom solutions.
	%TA
	 \vspace{-0.2in}  
	 \begin{tabbing}
	 \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
		{\bf Teaching Assistant} \>UMass - College of Computer Science    \>Jan 23, 2017 - Present\\
														 \>Amherst, MA
	 \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
		Assisted in administration of core computer science class as well as helped students one on one with homework, quizzes and projects for two semesters.
	% Amazon
	 \vspace{-0.2in}
	 \begin{tabbing}
	 \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
		{\bf Amazon Fufillment Associate} \>Amazon.com    \>June 6, 2016 - Sept 2, 2016\\
														 \>Robbinsville, NJ
	 \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
		Sorted products ordered off Amazon.com to various locations to be packaged and shipped out. Averaged over 1,200 products per hour, top associate.
	%Lead Team Programmer
	 \vspace{-0.2in}
	 \begin{tabbing}
		\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
		{\bf Lead Team Programmer} \>First Robotics Competition Team 1807 \>  Sept 2012 - June 2016 \\
			\>Allentown, NJ
	\end{tabbing}\vspace{-20pt}         % suppress blank line after tabbing
	Managed programming of multiple robots with each robot designed to complete a different task. Typically oversaw multiple new programmers with little to no experience
	and taught  them everything they needed to become a productive member of the team. 
	%NYLT
	\vspace{-0.2in}
	\begin{tabbing}
		\hspace{2.3in}\= \hspace{2.2in}\= \hspace{.4in}\= \kill % set up two tab positions          
		{\bf Leadership Staff Instructor}  \>BSA - NYLT \> Summer 2014, Summer 2015\\
		\>Manalapan Twp., NJ
	\end{tabbing}\vspace{-20pt}            % suppress blank line after tabbing
	Responsible for teaching leadership skills to a group of youths and managed activities done during the National Youth Leadership Training Conference in order to reinforce the concepts taught.
\vspace{-0.2in}
\section{COMPUTER SKILLS}          
		Extensive knowledge of Java, C, BASIC, Python, HTML, CSS, PHP, MySQL, Shell  \\ 
		Experience with C\#, NodeJS, Angular, AppleScript, Swift, C++, Scala, \LaTeX\\
		Web Design - Front End and Back End
\vspace{-0.2in}
\section{PROJECTS}
	www.CannaSense.com - Automation of tasks leading to a 150\% increase in overall productivity\\
		Redesigned and Maintained: 2016-Present\\
	www.RobertTrivers.com - Site for world renowned professor in evolutionary biology\\
		Created and Maintained: 2009-Present\\
	HW Reminder - App to keep track of assignments, coming soon to app store \\
		Created and Maintained 2016-Present\\
	More projects on GitHub - Handle: Normana10 (https://github.com/normana10)
\vspace{-0.2in}
\section{EXTRACURRICULAR ACTIVITIES AND AWARDS}          
		Boy Scouts of America: Troop 116 \\
		First Robotics Competition (FIRST) Team 1807 Member: 2011-2015 Mentor: 2015-Present\\
		Eagle Scout
\end{resume}
\end{document}






